Optimizing Abstract$^2$ Machines

### 2012-10-06 paper/paper.tex
Initial numbers in outline.

\begin{abstract}
The abstracting abstract machines approach to program analysis makes
it easy to design and implement sound and computable abstract
interpretations of higher-order programs.
%
However, the straightforward implementation is generally
not very fast.
%
This article contributes a step by step process for going from a naive
abstract$^2$ machine to an efficient program analyzer that is two
orders of magnitude faster than the starting point, yet just as
precise.
\end{abstract}
%
\section{Introduction}

\section{Starting point}
\subsection{An abstract$^2$ machine for PCF}
\subsection{An example: Analyzing Church number computations}
\subsection{Store widening}
\subsection{Baseline evaluation}

\section{Precision preserving recipe}
\subsection{Fixed-point specialization}
\subsection{Lazy non-determinism}
\subsection{Abstract compilation}
\subsection{Computing with store changes}

@@

>>>>

\begin{abstract}
The abstracting abstract machines approach to program analysis makes
it easy to design and implement sound and computable abstract
interpretations of higher-order programs.
%
However, the straightforward implementation is generally
not very fast.
%
This article contributes a step by step process for going from a naive
abstract$^2$ machine to an efficient program analyzer that is (nearly)
three orders of magnitude faster than the starting point, yet just as
precise (and purely functional).
\end{abstract}
%
\section{Introduction}

\section{Starting point}
\subsection{An abstract$^2$ machine for PCF}
\subsection{An example: Analyzing Church number computations}
\subsection{Store widening}

\subsection{Baseline evaluation}

Wide Store: cpu time: 551571 real time: 571319 gc time: 4003

\section{Precision preserving recipe}

\subsection{Lazy non-determinism}

Lazy:
   cpu time: 32481 real time: 32881 gc time: 547

\subsection{Abstract compilation}

Compile:
   cpu time: 255397 real time: 261532 gc time: 2947

\noindent
Compile + Lazy:
   cpu time: 31173 real time: 31642 gc time: 739

\subsection{Fixed-point specialization}

%% Should be commutted to beginning

Special + Compile + Lazy:
   cpu time: 14212 real time: 14681 gc time: 823

\subsection{Computing with store changes}

Delta Store + Special + Compile + Lazy:
   cpu time: 668 real time: 686 gc time: 41

@@

Other benchmarks
